Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-09-28 psy_peds_2.Rmd
updating currently hospitalized patient counts

### Total hospitalize patients
```{r, fig.height=12, fig.width=12}
total_hospitalizations_per_day <- all_codes %>%
  group_by(patient_num, date ) %>%
  filter(date < '2021-05-01' &
         date >= '2019-03-01' ) %>%
    group_by( date, weeks, month) %>%
  summarise(count = n_distinct(patient_num)) %>% 
  ungroup()

total_hospitalizations_per_week <- total_hospitalizations_per_day %>% 
  filter(weeks > '2019-03-01') %>% 
    group_by( weeks ) %>%
  summarise(count = sum(count))

total_hospitalizations_per_month <- total_hospitalizations_per_day %>%
  group_by( month ) %>%
  summarise(count = sum(count))

>>>>

### Total hospitalize patients
```{r, fig.height=12, fig.width=12}
total_hospitalizations_per_day <- all_codes %>%
  filter(date < '2021-05-01' &
         date >= '2019-03-01' ) %>%
    group_by( date ) %>%
  summarise(count = n_distinct(patient_num))

total_hospitalizations_per_week <- all_codes %>%
  filter(date < '2021-05-01' &
         date >= '2019-03-01' ) %>%
    group_by( weeks ) %>%
  summarise(count = n_distinct(patient_num))

total_hospitalizations_per_month <- all_codes %>%
  filter(date < '2021-05-01' &
         date >= '2019-03-01' ) %>%
    group_by( month ) %>%
  summarise(count = n_distinct(patient_num))
